---
title: "Untitled"
output: html_document
date: "2025-07-23"
---

## Fuentes de Informacion DataSets

1.  **PARAMETROS BUSQUEDA**

| Campos                | Valores                    |
|-----------------------|----------------------------|
| **Area de Gobierno:** | Economía y finanzas        |
| **Organizacion:**     | Secretaría de Planeamiento |
| **Tags:**             | Empleo / Empresas          |

2.  **DATASET SELECCIONADO**

-   **Archivo de Datos:** Distribución geográfica de los establecimientos productivos

```{r cars}

url_1 <- "https://cdn.produccion.gob.ar/cdn-cep/establecimientos-productivos/distribucion_establecimientos_productivos_sexo.csv"


```

geo_estab_produc \<- read_delim(url_1, delim = ",")

# ver estructura del dataset

glimpse(geo_estab_produc)

#colnames(geo_estab_produc)

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
